---
title: "Jared Garfinkel"
author: "Sustainability professional seeking a scientific role doing a public service."
date: "10/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE)
library(tidyverse)
```

```{r}
name = "Jared Garfinkel"
desc = "Sustainability professional seeking \n a scientific role doing a public service."
cell = "(516) 972-5348"
email = "jared.garfinkel@gmail.com"
address = "65 Cornell Drive \n Plainview, NY 11803-1834"
header = tibble(
  about = c(name, desc, address),
  contact = c("", cell, email)
)
```

```{r, fig.width = 12}
header %>% 
  knitr::kable(col.names = c("",""), format = "markdown", padding = 2)
```


|         |              |
| ------  | ------------ |
| cell    |$~~$ (516) 972-5348 |
| email   |$~~$ jared.garfinkel@gmail.com |
| address |$~~$ 65 Cornell Drive, Plainview, NY 11803 |
| LinkedIn |$~~$ https://www.linkedin.com/in/jaredgarfinkel

## Experience

Long Island Progressive Coalition, Massapequa, NY

May 2017 - present

Volunteer

* Grew connections to Long Island residents in an effort to align local- and state-level

    elected officials with climate action legislation.

* Led volunteer climate justice groups on Long Island.

***

IT Asset Management Group, Farmingdale, NY 

March 2019 - August 2019

Administrative Assistant

* Tracked up to twenty wholesale orders a month for an e-waste company.

* Processed checks and bills, followed up with accounts receivable and accounts payable, 

    purchased warehouse supplies from twenty vendors up to ten times a week. 
    
***

Veolia ES Technical Solutions, Wantagh, NY

March 2018 - December 2018

Environmental Specialist I

* Provided specialized transportation and disposal services to clients. 

***

National Center for Suburban Studies, Hempstead, NY

September2016 - May 2017

Graduate Research Intern

* Initiated a groundwater quality data research project for Long Island focusing 

    on 1,4-dioxane by analyzing over 500 points of previously collected water quality data. 

* Presented my report to the Nassau County Comptroller’s Environmental Advisory Working Group. 

***

National Center for Suburban Studies, Hempstead, NY

September 2013 - May 2014

Undergraduate Research Assistant

* Leveraging a first-time waste audit of an on-campus dining hall, successfully lobbied staff 

    and administrators to expand the plastic recycling program to over 100 buildings. 
    
* Coordinated the projects of three undergraduate students on food waste. 

## Education

Columbia University, New York, NY

Expected 2021

Master of Science in Biostatistics

***

Hofstra University, Hempstead, NY

May 2017

Master of Arts in Sustainability

* Thesis: Heavy Metals in Road Deposited Sediment in Town of Oyster Bay, Long Island, NY

* Outstanding Academic Achievement, Geology, Environment and Sustainability Department 2017

* Cumulative GPA: 3.67/4.0

***

Hofstra University, Hempstead, NY

May 2014

Bachelor of Science in Sustainability Studies; minors in Biology, Chemistry, and Mathematics