---
title: "Jared Garfinkel"
author: "Early career biostatistician"
date: "31 March 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE)
library(tidyverse)
```

```{r}
name = "Jared Garfinkel"
desc = "Data Analyst"
cell = "(516) 972-5348"
email = "jared.garfinkel@gmail.com"
address = "25 Cooper Street Apt 3A \n New York, NY 10034"
header = tibble(
  about = c(name, desc, address),
  contact = c("", cell, email)
)
```

```{r, fig.width = 12}
header %>% 
  knitr::kable(col.names = c("",""), format = "markdown", padding = 2)
```


|         |              |
| ------  | ------------ |
| email   |$~~$ jared.garfinkel@gmail.com |
| cell    |$~~$ (516) 972-5348 |
| address |$~~$ New York, NY 10034 |

***

## Research Experience

### Data Analyst, June 2022 --- present

##### NGO ICAP, New York, NY 10034

*  Provide data/statistical analysis and data visualizations in support of surveys related to HIV and hepatitis international infection rates spanning large populations (tens of thousands of 8  participants). 
*  Perform quality assurance assessments validating infection data against laboratory findings. 
*  Produced more than 20 dashboards using R packages. 
*  Coalesce data using Shiny to create interactive data visualizations that form the foundation of essential reports. 
*  Automate aspects of data visualization reports for efficiency. 
*  Deliver statistical programming expertise to projects. Update legacy code to specifications in SAS and summarize statistics in more than 20 tables. 
*  Merge data from eight different datasets in SAS, .xlsx, or .csv. This data is voluminous (50,000+ lines of code). 
*  Maintain a database for managing and tracking data discrepancies. 
*  Utilize Excel pivot tables and x-lookup to research and verify code. 
*  Wrote and periodically maintain a GitLab guide for colleagues.

### Data Analyst, October 2021 --- June 2022

##### Columbia University Mailman School of Public Health, New York, NY

*	Independently cleaned EHR data for exploratory data analysis (EDA) in R and SAS for descriptive statistics.
*	Understood data dictionaries for over 10 datasets with 10,000,000+ rows to operationalize variables.
*	Maintained version control of R Projects using GitHub.

### Graduate Data Science Summer Program (GDSSP), Summer 2021

##### National Institutes of Health (NIH), Remote

* Suggested statistical methods for sparse data that added value by reducing bias and removing complete- and quasi-separated logistic regression models.

### Practicum Field Work Report, July 2021 --- June 2021

##### ICAP at Columbia University, New York, NY

* Advisor: Dr. Stephen Delgado, Dr. Ying Wei, Giles Reid
  + Latent Variable Analysis
  + Bayesian Latent Class Analysis

*  Developed a statistical analysis plan for survey data in a 20,000 x 20 data frame. 
Using R Markdown, created bar graphs and maps using numerical and geographic data. This effort aided consultants hired to do complex analytical work.

### Sustainability Data Analyst, June 2020 --- July 2021		

##### The Mill River Project, Hempstead, NY							 	  

* For two projects (sustainability scorecard and community survey) cleansed data using R.

### Graduate Research Assistant, September 2016 --- May 2017

Sustainability Studies Program, Hempstead, NY, Dr. Sandra Garren

### Undergraduate Research Assistant, September 2013 --- May 2014

Sustainability Studies Program, Hempstead, NY, Dr. Robert Brinkmann

### Undergraduate Research Assistant,  November 2012 --- February 2013

SUNY Farmingdale Chemistry Department, Farmingdale, NY, Dr. Glen Hinckley

***

## Publications

Shah, Riddhi, et al. “Statins restore endothelial protection against complement activity in obstructive sleep apnea: A randomized clinical trial.” Annals of the American Thoracic Society, vol. 20, no. 7, 1 July 2023, pp. 1029–1037, https://doi.org/10.1513/annalsats.202209-761oc. 

## Computer Skills

Biostatistical Methods               | Applications
-------------------------------------|------------------------------------------------------------------------------------
Model Selection                      | RStudio and RMarkdown
Model diagnostics and fit statistics | GitHub and GitLab
Regression                           | Base SAS
Clustering                           | Microsoft Excel, Microsoft Word, Microsoft PowerPoint, Microsoft Outlook, Microsoft Access
Unsupervised learning techniques     | Python
Causal inference                     | ArcGIS
Bayesian analysis                    | 
Machine learning                     |

***

## Education

### Master of Science in Biostatistics, May 2021

##### Columbia University, New York, NY

* Chair's Award for Outstanding Master's Student, Biostatistics, 2021
* Practicum Field Work Report: “Measuring Uncertainty in a Standard Classification Procedure of Population-based HIV Assessment (PHIA) Survey Results”


### Master of Arts in Sustainability, May 2017

##### Hofstra University, Hempstead, NY

* Outstanding Academic Achievement, Geology, Environment and Sustainability Department 2017
* Thesis: “Heavy Metals in Road Deposited Sediment in Town of Oyster Bay, Long Island, New York” 
  + Committee: Dr. Sandra Garren, Dr. Kevin Bisceglia, Dr. Margaret Hunter


### Bachelor of Science in Sustainability Studies, May 2014

##### Hofstra University, Hempstead, NY

* Minors in Biology, Chemistry, and Mathematics
* First Graduate of the Sustainability Degree Program

***


## Honors and Awards

##### Chair’s Award for Outstanding Master’s Student, 2021

* Biostatistics Department, Columbia University Mailman School Of Public Health
  + Awarded to a master’s student based on the clarity and complexity of one’s Practicum Field Work Report

##### Outstanding Academic Achievement, 2017

* Geology, Environment, and Sustainability Department

***

## Professional Affiliations

American Statistical Association NYC Metro Chapter, 2021 --- Present

***

## Professional Experience

### Graduate Student Assistant, Data Management and Informatics Team

ICAP at Columbia, New York, NY, July 2020 --- June 2021

### Administrative Assistant

IT Asset Management Group, Farmingdale, NY March 2019 --- August 2019

### Administrative Assistant

Albert Einstein College of Medicine, Bronx, NY January 2019 --- March 2019

### Environmental Specialist I

Veolia ES Technical Solutions, Wantagh, NY March 2018 --- December 2018

### Customer Service Cashier

Target Corporation, Hicksville, NY	September 2017 --- March 2018

### Canvasser

Citizens Campaign for the Environment, Farmingdale, NY September 2014 --- November 2014

### Bakery Assistant

Maxi Cakes, Bellmore, NY December 2012 --- April 2013

***

## Community Service

### Volunteer Climate Organizer

Long Island Progressive Coalition, Massapequa, NY, May 2017 - May 2020

### Environmental and Climate Justice Working Group Chair 

Nassau County DSA, Plainview, NY, August 2019 --- June 2020

### Co-Founder/Coordinator

Sunrise Movement Long Island, Islip, NY, January 2019 --- October 2019

### Mentor for Advanced High School Students

West Hempstead High School, Hempstead, NY, September 2016 --- January 2017

### President

Graduate Residence Hall Student Council, Hempstead, NY, September 2015 --- December 2015

### Film Intern

Nassau County Soil and Water Conservation District, Jericho, NY, April 2015 --- July 2015

### Phone Bank Coordinator 

New Yorkers Against Fracking, Garden City, September 2014 --- November 2014

### President

Students for a Greener Hofstra, Hempstead, NY, October 2013 --- May 2014

### Founder/Vice President 

Sustainability Studies Club, Hempstead, NY, 2013-2014

***

## Languages

Language | Proficiency Level
---------|-----------------------------------------------------------
English  | Native Language
Spanish  | Novice Listener, Intermediate Speaker, Reading and Writing
Italian  | Intermediate Listener, Speaker, Reading and Writing

***

## Other

U.S. Citizen

***

## Presentations and Invited Lectures

#### “Helicobacter pylori Seropositivity, Pepsinogens and Circulating Inflammation Markers” 

NIH Graduate Data Science Summer Intern Poster Day, 3 August 2021

#### “Measuring Uncertainty in a Standard Classification Procedure of Population-based HIV Assessment (PHIA) Survey Results”

Columbia University Biostatistics Master of Science Practicum Presentation, 16 April 2021

#### “Intersectionality in the Environmental Movement” 

Long Island Climate Action Summit Workshop, 18 Jan 2020

#### “Heavy Metals in Road Deposited Sediment in Town of Oyster Bay, Long Island, New York”

Hofstra University Sustainability Master of Arts Thesis Defense 12 May 2017