---
title: "Jared Garfinkel"
author: "Biostatistics master's candidate seeking a scientific role doing a public service."
date: "08May2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = FALSE)
library(tidyverse)
```

```{r}
name = "Jared Garfinkel"
desc = "Sustainability professional seeking \n a scientific role doing a public service."
cell = "(516) 972-5348"
email = "jared.garfinkel@gmail.com"
address = "65 Cornell Drive \n Plainview, NY 11803-1834"
header = tibble(
  about = c(name, desc, address),
  contact = c("", cell, email)
)
```

```{r, fig.width = 12}
header %>% 
  knitr::kable(col.names = c("",""), format = "markdown", padding = 2)
```


|         |              |
| ------  | ------------ |
| email   |$~~$ jared.garfinkel@gmail.com |
| cell    |$~~$ (516) 972-5348 |
| address |$~~$ Plainview, NY 11803 |

***

## Education

### Columbia University, New York, NY

##### Master of Science in Biostatistics, May 2021

* Chair's Award for Outstanding Master's Student, Biostatistics, 2021

### Hofstra University, Hempstead, NY

##### Master of Arts in Sustainability, May 2017

* Outstanding Academic Achievement, Geology, Environment and Sustainability Department 2017

### Hofstra University, Hempstead, NY

##### Bachelor of Science in Sustainability Studies, May 2014

* Minors in Biology, Chemistry, and Mathematics

***

## Experience

### Student Assistant, Data Management and Informatics, July 2020 - present

##### ICAP at Columbia University, New York, NY

* Translated data into an actionable solution to reduce data collection time-cost measures by 30% by potentially cutting an expensive blood test from a data collection protocol.

* Developed a statistical analysis plan (SAP) to calculate prevalence, sensitivity and specificity of public health survey data in a 20,000 by 20 dataframe using latent class analysis in randomLCA in R.

* Created 7 weighted summary tables and 4 figures using tidyverse and survey packages in R to improve negotiations with outside contractors on summary sheets by 15%.

* Presented a visualization of the locations of 200 outstanding returns on country maps to the team using GIS tools in R to assess the situation on the ground in over 40 districts in 3 countries.

### Project Management Intern, June 2020 - present		

##### The Mill River Project, Hempstead, NY							 	  

* Took charge of a community resilience survey design related to COVID-19 to collect 100 resident opinions for future research and public education about emergency preparedness communication.

* Delivered an Institutional Review Board (IRB) protocol 1 week ahead of schedule.

* Coordinated tasks between 2 teams on 4 research projects to meet deadlines.

* Coached 3 high school students on survey data projects for 6 weeks to improve learning objectives.

### Volunteer Climate Organizer, May 2017 - May 2020 	        

##### Long Island Progressive Coalition, Massapequa, NY

* Persuaded 6 state-level elected officials to vote in favor of climate action legislation.

* Led group discussions at monthly meetings and spoke at 4 lobby sessions with elected officials.

* Facilitated 2 climate justice groups to influence community members to commit to volunteer for climate justice on Long Island by promoting coalition building with New York Renews.

* Addressed a crowd of 2,000 people at a rally to deliver a land acknowledgement at the county legislature representing Sunrise Long Island.

### Administrative Assistant, March 2019 – August 2019 

##### IT Asset Management Group, Farmingdale, NY

*	Managed twenty wholesale orders a month for a computer refurbishing company.

*	Handled logistics for up to five shipments a day, followed up with accounts receivable and accounts payable, and processed regulatory documentation.

### Administrative Assistant, January 2019 - March 2019 

##### Albert Einstein College of Medicine, Bronx, NY

*	Answered phones, scheduled appointments, and maintained files and databases for the Department of Environmental Health and Safety.

### Environmental Specialist I, March 2018 – December 2018 

##### Veolia ES Technical Solutions, Wantagh, NY

*	Provided specialized transportation and disposal services to clients. 

### Customer Service Cashier, September 2017 – March 2018 

##### Target Corporation, Hicksville, NY

*	Used the POS system to process sales at a +10,000 sq. ft. retail store during the holiday season. 

*	Returned items and answered phones at the customer service desk. 

### Graduate Research Intern, September 2016 - May 2017

##### National Center for Suburban Studies, Hempstead, NY

* Generated a groundwater quality data research project using statistical analysis of 500 data points.

* Recommended a public health solution to the Nassau County Comptroller’s Environmental Advisory Working Group that would reduce a harmful chemical found in drinking water by 50%.